Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-10-22 draft.tex
bc

Before stating the definition of this model, we introduce the following variant of the de Rham complex of differential forms on $\RR_{\geq 0}$. 
Let $j : \RR_{>0} \hookrightarrow \RR_{\geq 0}$ be the embedding of the open ray into the closed ray. 
Let $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ be the two-term complex
\[
\Omega^0(\RR_{\geq 0}) \xto{j^* \circ \d_{\rm dR}} \Omega^1(\RR_{>0})[-1]  .
\]
The dg commutative algebra structure on $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ is defined by the formula
\[
f \cdot (g \, \d t) = (j^* f) g\, \d t .
\]

\begin{dfn}
\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the constructible factorization algebra on $M \times \RR_{\geq 0}$ where
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex 
\[
\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg), 
\]
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex 
\[
\bC_n (\fg) (V \times [0,\epsilon)) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon))[2] \right) \bigg).
\]
%\brian{this is wrong
%\[
%\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
%\]
%}
\end{itemize}
The structure map associated to the embedding 
\begin{equation}\label{eqn:embed}
i : U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
\end{equation}
is given by the composition
\[
\begin{tikzcd}
\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  \clies\bigg(\fg \otimes \Omega^\bu(V) \otimes \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon))[2] \right) \bigg) \ar[d, "\simeq"] \\
\clies \bigg(\fg \otimes \left(\Omega^\bu (U) \oplus \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \right) \; , \; \Sym \left(\fg \otimes \left(\Omega^\bu_c(U) [2] \oplus \Omega^\bu_c(V \times [0,\epsilon)) [2]\right)\right) \bigg) \ar[d, "i^* \otimes i_*"] \\
\clies\bigg(\fg \otimes \Omega^\bu(V') \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon'))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V' \times [0,\epsilon'))[2] \right) \bigg).
\end{tikzcd}
\]
%\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d, "\simeq"] \\
%\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d, "i_*"]\\
%\Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
The first map uses the fact that the symmetric algebra functor is symmetric monoidal. 
The second map is induced from restriction and extension of de Rham forms and compactly supported de Rham forms along the embedding~(\ref{eqn:embed}). 
\end{dfn}

@@

Next, we define the $\PP_0$-bracket for the value of the factorization algebra on open sets of the form $V \times [0,\epsilon)$. 
Notice that the underlying graded vector space of $\bC_n(\fg)(V \times [0,\epsilon))$ is of the form
\[
{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (V) \otimes \Tilde{\Omega}^\bu ([0,\epsilon))) [1]) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2] \right) \right)  .
\]
We first define the bracket $\{F,G\}$ between the following simple elements 
\[
F : \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \to k
\]
and 
\[
G : k \to \fg \otimes \Omega^\bu_c(V \times [0,\epsilon))[2] .
\]
Define $\{F, G\}$ by the composition
\[
\begin{tikzcd}
k \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[rdd, dotted, "{\{F,G\}}"'] \ar[r, "G \otimes 1"] & 
\bigg(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2]\bigg) \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[d,"{[\cdot, \cdot] \otimes \wedge}"] \\
& \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \ar[d, "F"] \\ & k
\end{tikzcd}
\]
The middle bracket is induced from the Lie bracket on $\fg$ and the wedge product of differential forms.
Again, this bracket is extended to the full algebra by the Leibniz rule.
\end{proof}

@@

Recall that for $V \subset M$ we have
\[
\bC_n(\fg)^\partial (V) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) .
\]
On $V$, the map $I^\partial$ is defined by the composition
\[
\begin{tikzcd}
\clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) \ar[r, "{{\rm ev}_1}"] & \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \ar[d, "{\int_{\RR_{\geq 0}}}"] \\ &  \Sym\left(\fg \otimes \Omega^\bu_c (V)[1] \right) .
\end{tikzcd}
\]
The first map ${\rm ev}_1$ evaluates the unit in $\Sym \left(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})\right)$ and the second map is induced by integration along $\RR_{\geq 0}$. 
It is quick to check that $I^{\partial}$ extends to a map of factorization algebras.

>>>>

Before stating the definition of this model, we introduce the following variants of the de Rham complex of differential forms on $\RR_{\geq 0}$ and compactly supported differential forms.

Let $j : \RR_{>0} \hookrightarrow \RR_{\geq 0}$ be the embedding of the open ray into the closed ray. 
Let $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ be the two-term complex
\[
\Omega^0(\RR_{\geq 0}) \xto{j^* \circ \d_{\rm dR}} \Omega^1(\RR_{>0})[-1]  .
\]
The dg commutative algebra structure on $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ is defined by the formula
\[
f \cdot (g \, \d t) = (j^* f) g\, \d t .
\]

Next, let $\Tilde{\Omega}^{\bu}_{c}(\RR_{\geq 0}) \subset \Omega^{\bu}_{c}(\RR_{\geq 0})$ be the sub dg algebra of compactly supported de Rham forms defined by
\[
\Tilde{\Omega}^{\bu}_{c}(\RR_{\geq 0}) = \{\alpha_{0} + \alpha_{1} \d t \; | \; \alpha_{0} (t = 0) = 0 \} .
\]

\begin{dfn}
\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the constructible factorization algebra on $M \times \RR_{\geq 0}$ where
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex 
\[
\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg), 
\]
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex 
\[
\bC_n (\fg) (V \times [0,\epsilon)) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V) \Hat{\otimes} \Tilde{\Omega}_{c}([0,\epsilon))[2] \right) \bigg).
\]
%\brian{this is wrong
%\[
%\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
%\]
%}
\end{itemize}
The structure map associated to the embedding 
\begin{equation}\label{eqn:embed}
i : U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
\end{equation}
is given by the composition
\[
\begin{tikzcd}
\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  \clies\bigg(\fg \otimes \Omega^\bu(V) \otimes \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V) \Hat{\otimes} \Tilde{\Omega}_{c}([0,\epsilon))[2] \right) \bigg) \ar[d, "\simeq"] \\
\clies \bigg(\fg \otimes \left(\Omega^\bu (U) \oplus \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \right) \; , \; \Sym \left(\fg \otimes \left(\Omega^\bu_c(U) [2] \oplus \Omega^\bu_c(V) \Hat{\otimes} \Tilde{\Omega}_{c}^{\bu}([0,\epsilon)) [2]\right)\right) \bigg) \ar[d, "i^* \otimes i_*"] \\
\clies\bigg(\fg \otimes \Omega^\bu(V') \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon'))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V') \Hat{\otimes} \Tilde{\Omega}^{\bu}_{c}([0,\epsilon'))[2] \right) \bigg).
\end{tikzcd}
\]
%\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d, "\simeq"] \\
%\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d, "i_*"]\\
%\Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
The first map uses the fact that the symmetric algebra functor is symmetric monoidal. 
The second map is induced from restriction and extension of de Rham forms and compactly supported de Rham forms along the embedding~(\ref{eqn:embed}). 
\end{dfn}

@@

Next, we define the $\PP_0$-bracket for the value of the factorization algebra on open sets of the form $V \times [0,\epsilon)$. 
Notice that the underlying graded vector space of $\bC_n(\fg)(V \times [0,\epsilon))$ is of the form
\[
{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (V) \otimes \Tilde{\Omega}^\bu ([0,\epsilon))) [1]) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2] \right) \right)  .
\]
We first define the bracket $\{F,G\}$ between the following simple elements 
\[
F : \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \to k
\]
and 
\[
G : k \to \fg \otimes \Omega^\bu_c(V \times [0,\epsilon))[2] .
\]
Define $\{F, G\}$ by the composition
\[
\begin{tikzcd}
k \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[rdd, dotted, "{\{F,G\}}"'] \ar[r, "G \otimes 1"] & 
\bigg(\fg \otimes \Omega^\bu_c(V) \Hat{\otimes} \Tilde{\Omega}^{\bu}_{c}([0,\epsilon)) [2]\bigg) \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[d,"{[\cdot, \cdot] \otimes \wedge}"] \\
& \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \ar[d, "F"] \\ & k
\end{tikzcd}
\]
The middle bracket is induced from the Lie bracket on $\fg$ and the wedge product of differential forms.
Again, this bracket is extended to the full algebra by the Leibniz rule.
\end{proof}

@@

Recall that for $V \subset M$ we have
\[
\bC_n(\fg)^\partial (V) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V) \Hat{\otimes} \Tilde{\Omega}_{c}^{\bu}(\RR_{\geq 0})[2] \right) \bigg) .
\]
On $V$, the map $I^\partial$ is defined by the composition
\[
\begin{tikzcd}
\clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) \ar[r, "{{\rm ev}_1}"] & \Sym\left(\fg \otimes \Omega^\bu_c (V) \Hat{\otimes} \Tilde{\Omega}_{c}^{\bu}(\RR_{\geq 0})[2] \right) \ar[d, "{\int_{\RR_{\geq 0}}}"] \\ &  \Sym\left(\fg \times \Omega^\bu_c (V)[1] \right) .
\end{tikzcd}
\]
The first map ${\rm ev}_1$ evaluates the unit in $\Sym \left(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})\right)$ and the second map is induced by integration along $\RR_{\geq 0}$. 
It is quick to check that $I^{\partial}$ extends to a map of factorization algebras.
